Type-Safe Modular Parsing

### 2016-12-16 paper/sections/OpenRecursion.tex
local changes

\section{Open Recursion and Parsing}\label{sec:openandparsing}

Our story begins with a well-known concept mostly in object-oriented programming, called \textit{open recursion}. This mechanism
constructs the basis of extensibility of our parsing. We will introduce the concept with illustration before integrating
it  to achieve halfway extensible parsers.

\subsection{Open Recursion with Delegation}\label{subsec:openrecursion}

@@

\lstinputlisting[linerange=27-30]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIX

where function \lstinline{f} has a by-name parameter of type \lstinline{"=>} \lstinline{A"}.
Here we illustrate by the famous Fibonacci example. Traditionally it can be implemented in Scala using pattern-matching:
\begin{lstlisting}
def fib : Int => Int = i => i match {
    case 0 => 0
    case 1 => 1
    case n => fib(n - 1) + fib(n - 2)
}

>>>>

\section{Delegation-based Parsing}\label{sec:openandparsing}

The first problem that prevents modularity of parsers built with
parser combinators is the existence of \emph{hard-coded recursive
  calls}. To solve this problem, \name employs \emph{open recursion}:
that is, recursive calls to parsers are parametrized. The resulting
programming style is similar to object-oriented programming, 
but using delegation instead of class-based inheritance.

\subsection{Delegation via Open Recursion}\label{subsec:openrecursion}

@@

\begin{lstlisting}
def fix[A](f : (=> A) => A) : A = {
    lazy val a : A = f(a)
    a
}
\end{lstlisting}
where function \lstinline{f} has a by-name parameter of type
\lstinline{"=>} \lstinline{A"}.  Here we illustrate by the famous
Fibonacci example. Traditionally it can be implemented in Scala using
pattern-matching:

\begin{lstlisting}
def fib : Int => Int = i => i match {
    case 0 => 0
    case 1 => 1
    case n => fib(n - 1) + fib(n - 2)
}
